Determinism, Complexity, and Predictability in Computer Performance

### 2014-07-18 results.tex
adding alert to update text based on table typo

The WPE of \gcc is higher still: $0.943 \pm 0.001$.  This system
transmits very little information forward in time and provides almost
no structure for prediction methods to work with.  Here, the \naive
~method performs best ($MASE=0.951 \pm 0.001$), simply because its
calculation of the mean filters out the noise in the signal.  Since
fitting a hyperplane using least squares should have similar effects,
the fact that LMA outperforms \arima ($1.530 \pm 0.021$ vs. $1.837
\pm 0.016$) is somewhat counterintuitive.  However, the small amount
of predictive structure that is present in this signal is nonlinear
(cf.,~\cite{mytkowicz09}), and LMA is designed to capture and exploit
that kind of structure.

>>>>

The WPE of \gcc is higher still: $0.943 \pm 0.001$.  This system
transmits very little information forward in time and provides almost
no structure for prediction methods to work with.  \alert{This needs to be reworded to reflect the typo, \naive is no longer the winner. MASE is $1.797 \pm 0.010$, rw actually wins $MASE = 1.1381 \pm 0.011$  Here, the \naive
~method performs best ($MASE=0.951 \pm 0.001$), simply because its
calculation of the mean filters out the noise in the signal.  Since
fitting a hyperplane using least squares should have similar effects,
the fact that LMA outperforms \arima ($1.530 \pm 0.021$ vs. $1.837
\pm 0.016$) is somewhat counterintuitive.  However, the small amount
of predictive structure that is present in this signal is nonlinear
(cf.,~\cite{mytkowicz09}), and LMA is designed to capture and exploit
that kind of structure.}
